The print method for class ranktable

### 2020-10-26 inst/ordertable_to_ranktable.Rmd
more work and rephrasing

Object `a` is a straightforward order table, just like
`skating_table`; we see, for example, that both judges put competitor
`a` first, but put `b` second and fifth respectively.  The judges
second choice was `b` and `c` respectively.  We can coerce order table
`OT` to a rank table `RT`:

@@

Object `RT` gives the same information but in a different form.  Note
that above we see the print method in action, which uses
`ranktable_to_printable_object()`.  However, it is possible to view
`RT` directly by removing class `ranktable`:

@@

Note carefully that the second row of `RT` (which corresponds to the
second judge) does *not* match the second column of `OT`.  The way to
read the second row of `RT` is as follows.  We see the entries `1 3 4
5 2` indicating that the first choice was competitor 1 [viz `a`, the
second choice competitor 3 [viz `c`], the third choice competitor 4
[viz `d`], fourth choice competitor 5 [`e`] and fifth choice
competitor 2 [`b`].  So the rows are *ranks* (see the discussion in
`rrank.Rd`).  But it is very tempting to read the second row of `RT`
as "judge 2 placed competitor `b` in third place", which is wrong
because this is interpreting the row as an *order*.  This is why the
print method is there.

>>>>

Object `OT` is a straightforward order table, just like
`skating_table` but smaller and simpler.  We have two columns, one for
each judge (named `J1` and`J2`), and five competitors, `a` through
`e`.  The first row refers to competitor `a`; both judges put
competitor `a` first.  The second row shows that `J1` put `b` second
and `J2` put competitor `b` fifth.  If instead we ask who was placed
third by each judge, this is not directly given; but by looking for
`3` in the table we see that `J1` put `c` third and `J2` put `d`
third.  To answer this and similar questions directly, we can coerce
order table `OT` to a rank table `RT`:

@@

Object `RT` gives the same information as `OT` but in a different
form.  Note that above we see the print method in action, which uses
`ranktable_to_printable_object()`.  Here the _rows_ correspond to the
two judges.  Each row is a rank vector.  Column headings refer to
placings (`c1` is supposed to be read "came first", `c2` "came second"
etc).  Looking at the fifth column (`c5`) we see that `J1` and `J2`
placed `e` and `b` fifth respectively.

Note that it is possible to view object `RT` directly by removing
class `ranktable`:

@@

Note carefully that the second row of `RT` (which corresponds to the
second judge) does *not* match the second column of `OT`.  The way to
read the second row of `RT` is as follows.  We see the entries `1 3 4
5 2` indicating that the first choice was competitor 1 [viz `a`], the
second choice was competitor 3 [viz `c`], the third choice was
competitor 4 [viz `d`], fourth choice was competitor 5 [`e`] and fifth
choice was competitor 2 [`b`].  So the rows are *ranks* (see the
discussion in `rrank.Rd`).  But it is very tempting to read the second
row of `RT` as "judge 2 placed competitor `b` in third place", which
is wrong because this is interpreting the row as an *order*.  This is
why the print method is there.
